Russian sanctions figures

### 2024-03-14 ms-russia-figures.Rmd
figure edits

# ARTIS dataframe
artis <- dbGetQuery(con, "SELECT * FROM all_estimates_snet") %>%
  select(-record_id)

@@

```{r}
# Consumption of Russian products by sanctioning and non-sanctioning countries, colored by import path (direct vs indirect)
# Fill version
consumption %>%
  filter(consumer_iso3c != "RUS", 
         source_country_iso3c == "RUS") %>%
  mutate(path = case_when(
    exporter_iso3c == "RUS" ~ "Direct import", 
    TRUE ~ "Import from intermediate partner"
  )) %>% 
  group_by(year, path, sanctions_towards_russia) %>%
  summarise(consumption_live_t = sum(consumption_live_t)) %>%
  ggplot(aes(x = year, y = consumption_live_t/1000000, fill = path)) +
  geom_area() +
  geom_vline(aes(xintercept = 2014), linetype = 2) +
  scale_fill_manual(values = c("#D4B95f", # khaki
                               "#4FA2A2" # teal
  )) + 
  labs(x = "", y = "Consumption of Russian seafood \n(mil t, live weight)", fill = "") +
  facet_wrap(~sanctions_towards_russia) +
  theme_minimal() +
  theme(legend.position = "bottom") # FIXIT: year labels shouldn't overlap

# Consumption of Russian products by sanctioning and non-sanctioning countries, colored by import path (direct vs indirect)
# Line version
consumption %>%
  filter(consumer_iso3c != "RUS", 
         source_country_iso3c == "RUS") %>%
  mutate(path = case_when(
    exporter_iso3c == "RUS" ~ "Direct import", 
    TRUE ~ "Import from intermediate partner"
  )) %>% 
  group_by(year, path, sanctions_towards_russia) %>%
  summarise(consumption_live_t = sum(consumption_live_t)) %>%
  ggplot(aes(x = year, y = consumption_live_t/1000000, color = path)) +
  geom_line() +
  geom_vline(aes(xintercept = 2014), linetype = 2) +
  scale_color_manual(values = c("#D4B95f", # khaki
                               "#4FA2A2" # teal
  )) + 
  labs(x = "", y = "Consumption of Russian seafood \n(mil t, live weight)", color = "") +
  facet_wrap(~sanctions_towards_russia) +
  theme_minimal() +
  theme(legend.position = "bottom") # FIXIT: year labels shouldn't overlap

@@

```{r}
# Russian consumption of seafood products from sanctioning and non-sanctioning countries, colored by import path (direct vs indirect)
# Fill version
consumption %>%
  filter(consumer_iso3c == "RUS", 
         source_country_iso3c != "RUS") %>%
  mutate(path = case_when(
    source_country_iso3c == exporter_iso3c ~ "Direct import", 
    TRUE ~ "Import from intermediate partner"
  )) %>% 
  group_by(year, path, source_sanctions_towards_russia) %>%
  summarise(consumption_live_t = sum(consumption_live_t)) %>%
  ggplot(aes(x = year, y = consumption_live_t/1000000, fill = path)) +
  geom_area() +
  geom_vline(aes(xintercept = 2014), linetype = 2) +
  scale_fill_manual(values = c("#D4B95f", # khaki
                               "#4FA2A2" # teal
  )) + 
  labs(x = "", y = "Russian consumption of foreign seafood \n(mil t, live weight)", fill = "") +
  facet_wrap(~source_sanctions_towards_russia) +
  theme_minimal() +
  theme(legend.position = "bottom") # FIXIT: year labels shouldn't overlap

# Russian consumption of seafood products from sanctioning and non-sanctioning countries, colored by import path (direct vs indirect)
# Line version
consumption %>%
  filter(consumer_iso3c == "RUS", 
         source_country_iso3c != "RUS") %>%
  mutate(path = case_when(
    source_country_iso3c == exporter_iso3c ~ "Direct import", 
    TRUE ~ "Import from intermediate partner"
  )) %>% 
  group_by(year, path, source_sanctions_towards_russia) %>%
  summarise(consumption_live_t = sum(consumption_live_t)) %>%
  ggplot(aes(x = year, y = consumption_live_t/1000000, color = path)) +
  geom_line() +
  geom_vline(aes(xintercept = 2014), linetype = 2) +
  scale_color_manual(values = c("#D4B95f", # khaki
                               "#4FA2A2" # teal
  )) + 
  labs(x = "", y = "Russian consumption of foreign seafood \n(mil t, live weight)", color = "") +
  facet_wrap(~source_sanctions_towards_russia) +
  theme_minimal() +
  theme(legend.position = "bottom") # FIXIT: year labels shouldn't overlap

@@

@@

# Top species US consumes sourced from Russia
species_rank <- consumption %>%
  filter(consumer_iso3c == "USA", source_country_iso3c == "RUS", year %in% 2015:2019) %>%
  mutate(path = case_when(
    exporter_iso3c == "RUS" ~ "Direct import", 
    TRUE ~ "Import from intermediate partner"
  )) %>% 
  rename("importer_iso3c" = "consumer_iso3c",
         "live_weight_t" = "consumption_live_t") %>%
  plot_bar(bar_group = "common_name_hs_modified", fill_type = "path") + 
  theme(legend.position = "bottom")

@@

```{r}
rus_to_chn <- artis %>%
  filter(source_country_iso3c == "RUS", exporter_iso3c == "RUS", importer_iso3c == "CHN") %>%
  group_by(year, sciname) %>%
  summarise(russia_live_t = sum(live_weight_t, na.rm = TRUE))

notrus_to_chn <- artis %>%
  filter(source_country_iso3c != "RUS", exporter_iso3c != "RUS", importer_iso3c == "CHN") %>%
  group_by(year, sciname) %>%
  summarise(notrussia_live_t = sum(live_weight_t, na.rm = TRUE))

@@

# FIXIT: This can be streamlined to not repeat code
p1 <- artis %>%
  filter(source_country_iso3c == "RUS", exporter_iso3c == "CHN", importer_iso3c == "USA") %>%
  group_by(year, sciname) %>%
  summarise(live_weight_t = sum(live_weight_t, na.rm = TRUE)) %>% 
  filter(sciname == "gadus chalcogrammus") %>%
  left_join(chn_to_usa %>%
              select(year, sciname, min_russia, max_russia)) %>% 
  ggplot(aes(x = year)) +
  geom_ribbon(aes(ymin = min_russia, ymax = max_russia), fill = "#86ADA7", alpha = 0.5) +
  geom_line(aes(y = live_weight_t)) +
  labs(x = "", y = "tonnes, live weight", title = "US imports of Russian Alaska pollock via China") +
  theme_bw()

p2 <- artis %>%
  filter(source_country_iso3c == "RUS", exporter_iso3c == "CHN", importer_iso3c == "USA") %>%
  group_by(year, sciname) %>%
  summarise(live_weight_t = sum(live_weight_t, na.rm = TRUE)) %>% 
  filter(sciname == "oncorhynchus gorbuscha") %>%
  left_join(chn_to_usa %>%
              select(year, sciname, min_russia, max_russia)) %>% 
  ggplot(aes(x = year)) +
  geom_ribbon(aes(ymin = min_russia, ymax = max_russia), fill = "#86ADA7", alpha = 0.5) +
  geom_line(aes(y = live_weight_t)) +
  labs(x = "", y = "tonnes, live weight", title = "US imports of Russian pink salmon via China") +
  theme_bw()

p3 <- artis %>%
  filter(source_country_iso3c == "RUS", exporter_iso3c == "CHN", importer_iso3c == "USA",
         year > 1996) %>%
  group_by(year, sciname) %>%
  summarise(live_weight_t = sum(live_weight_t, na.rm = TRUE)) %>% 
  filter(sciname == "gadus morhua") %>%
  left_join(chn_to_usa %>%
              select(year, sciname, min_russia, max_russia)) %>% 
  ggplot(aes(x = year)) +
  geom_ribbon(aes(ymin = min_russia, ymax = max_russia), fill = "#86ADA7", alpha = 0.5) +
  geom_line(aes(y = live_weight_t)) +
  labs(x = "", y = "tonnes, live weight", title = "US imports of Russian Atlantic cod via China") +
  theme_bw()

p4 <- artis %>%
  filter(source_country_iso3c == "RUS", exporter_iso3c == "CHN", importer_iso3c == "USA",
         year > 1996) %>%
  group_by(year, sciname) %>%
  summarise(live_weight_t = sum(live_weight_t, na.rm = TRUE)) %>% 
  filter(sciname == "melanogrammus aeglefinus") %>%
  left_join(chn_to_usa %>%
              select(year, sciname, min_russia, max_russia)) %>% 
  ggplot(aes(x = year)) +
  geom_ribbon(aes(ymin = min_russia, ymax = max_russia), fill = "#86ADA7", alpha = 0.5) +
  geom_line(aes(y = live_weight_t)) +
  labs(x = "", y = "tonnes, live weight", title = "US imports of Russian haddock via China") +
  theme_bw()

p5 <- artis %>%
  filter(source_country_iso3c == "RUS", exporter_iso3c == "CHN", importer_iso3c == "USA",
         year > 1996) %>%
  group_by(year, sciname) %>%
  summarise(live_weight_t = sum(live_weight_t, na.rm = TRUE)) %>% 
  filter(sciname == "gadus macrocephalus") %>%
  left_join(chn_to_usa %>%
              select(year, sciname, min_russia, max_russia)) %>% 
  ggplot(aes(x = year)) +
  geom_ribbon(aes(ymin = min_russia, ymax = max_russia), fill = "#86ADA7", alpha = 0.5) +
  geom_line(aes(y = live_weight_t)) +
  labs(x = "", y = "tonnes, live weight", title = "US imports of Russian Pacific cod via China") +
  theme_bw()

p_joined <- ggarrange(p1, p2, p3, p4, ncol = 1)

@@

>>>>

# ARTIS dataframe
artis <- dbGetQuery(con, "SELECT * FROM snet") %>%
  select(-record_id)

@@

```{r}
# Consumption of Russian products by sanctioning and non-sanctioning countries, colored by import path (direct vs indirect)
# Fill version
consumption_of_rus_p <- consumption %>%
  filter(consumer_iso3c != "RUS", 
         source_country_iso3c == "RUS") %>%
  mutate(path = case_when(
    exporter_iso3c == "RUS" ~ "Direct import", 
    TRUE ~ "Import from intermediate partner"
  )) %>% 
  group_by(year, path, sanctions_towards_russia) %>%
  summarise(consumption_live_t = sum(consumption_live_t)) %>%
  ggplot(aes(x = year, y = consumption_live_t/1000000, fill = path)) +
  geom_area() +
  geom_vline(aes(xintercept = 2014), linetype = 2) +
  scale_fill_manual(values = c("#D4B95f", # khaki
                               "#4FA2A2" # teal
  )) + 
  labs(x = "", y = "Consumption of Russian seafood \n(mil t, live weight)", fill = "") +
  facet_wrap(~sanctions_towards_russia) +
  theme_minimal() +
  theme(
    axis.title.y = element_text(size = 9),
    legend.position = "top",
    panel.spacing = unit(5, "mm")
  )

consumption_of_rus_p

# Consumption of Russian products by sanctioning and non-sanctioning countries, colored by import path (direct vs indirect)
# Line version
consumption %>%
  filter(consumer_iso3c != "RUS", 
         source_country_iso3c == "RUS") %>%
  mutate(path = case_when(
    exporter_iso3c == "RUS" ~ "Direct import", 
    TRUE ~ "Import from intermediate partner"
  )) %>% 
  group_by(year, path, sanctions_towards_russia) %>%
  summarise(consumption_live_t = sum(consumption_live_t)) %>%
  ggplot(aes(x = year, y = consumption_live_t/1000000, color = path)) +
  geom_line() +
  geom_vline(aes(xintercept = 2014), linetype = 2) +
  scale_color_manual(values = c("#D4B95f", # khaki
                               "#4FA2A2" # teal
  )) + 
  labs(x = "", y = "Consumption of Russian seafood \n(mil t, live weight)", color = "") +
  facet_wrap(~sanctions_towards_russia) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    panel.spacing = unit(5, "mm")
  )

@@

```{r}
# Russian consumption of seafood products from sanctioning and non-sanctioning countries, colored by import path (direct vs indirect)
# Fill version
rus_foreign_consumption_p <- consumption %>%
  filter(consumer_iso3c == "RUS", 
         source_country_iso3c != "RUS") %>%
  mutate(path = case_when(
    source_country_iso3c == exporter_iso3c ~ "Direct import", 
    TRUE ~ "Import from intermediate partner"
  )) %>% 
  group_by(year, path, source_sanctions_towards_russia) %>%
  summarise(consumption_live_t = sum(consumption_live_t)) %>%
  ggplot(aes(x = year, y = consumption_live_t/1000000, fill = path)) +
  geom_area() +
  geom_vline(aes(xintercept = 2014), linetype = 2) +
  scale_fill_manual(values = c("#D4B95f", # khaki
                               "#4FA2A2" # teal
  )) + 
  labs(x = "", y = "Russian consumption of foreign seafood \n(mil t, live weight)", fill = "") +
  facet_wrap(~source_sanctions_towards_russia) +
  theme_minimal() +
  theme(
    axis.title.y = element_text(size = 9),
    legend.position = "top",
    panel.spacing = unit(5, "mm")
  )

rus_foreign_consumption_p

# Russian consumption of seafood products from sanctioning and non-sanctioning countries, colored by import path (direct vs indirect)
# Line version
consumption %>%
  filter(consumer_iso3c == "RUS", 
         source_country_iso3c != "RUS") %>%
  mutate(path = case_when(
    source_country_iso3c == exporter_iso3c ~ "Direct import", 
    TRUE ~ "Import from intermediate partner"
  )) %>% 
  group_by(year, path, source_sanctions_towards_russia) %>%
  summarise(consumption_live_t = sum(consumption_live_t)) %>%
  ggplot(aes(x = year, y = consumption_live_t/1000000, color = path)) +
  geom_line() +
  geom_vline(aes(xintercept = 2014), linetype = 2) +
  scale_color_manual(values = c("#D4B95f", # khaki
                               "#4FA2A2" # teal
  )) + 
  labs(x = "", y = "Russian consumption of foreign seafood \n(mil t, live weight)", color = "") +
  facet_wrap(~source_sanctions_towards_russia) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    panel.spacing = unit(5, "mm")
  )

@@

```{r fig.height = 6, width = 8}
# Format figure 1 together
ggarrange(
  consumption_of_rus_p,
  rus_foreign_consumption_p,
  nrow = 2,
  common.legend = TRUE
)

ggsave("fig1.png", device = "png", height = 5, width = 6.5, units = "in")
```

@@

# Top species US consumes sourced from Russia
species_rank <- consumption %>%
  filter(consumer_iso3c == "USA", source_country_iso3c == "RUS", year %in% 2015:2019) %>%
  mutate(path = case_when(
    exporter_iso3c == "RUS" ~ "Direct import", 
    TRUE ~ "Import from\nintermediate partner"
  )) %>% 
  rename("importer_iso3c" = "consumer_iso3c",
         "live_weight_t" = "consumption_live_t") %>%
  mutate(common_name_hs_modified = case_when(
    common_name_hs_modified == "alaska pollock(=walleye poll.)" ~ "Alaska Pollock",
    common_name_hs_modified == "atlantic cod" ~ "Atlantic Cod",
    common_name_hs_modified == "pink(=humpback) salmon" ~ "Pink Salmon",
    common_name_hs_modified == "haddock" ~ "Haddock",
    common_name_hs_modified == "pacific cod" ~ "Pacific Cod",
    TRUE ~ common_name_hs_modified
  )) %>%
  mutate(common_name_hs_modified = gsub(" ", "\n", common_name_hs_modified)) %>%
  plot_bar(bar_group = "common_name_hs_modified", fill_type = "path", top_n = 5) + 
  theme(
    legend.position = "bottom",
    axis.text.y = element_text(angle = 90),

  ) +
  labs(y = "", x = "Consumption (live weight tonnes)", fill = "")

@@

```{r}
rus_to_chn <- artis %>%
  # Isolating Chinese imports that were originally caught in Russia
  filter(source_country_iso3c == "RUS", importer_iso3c == "CHN") %>%
  group_by(year, sciname) %>%
  summarise(russia_live_t = sum(live_weight_t, na.rm = TRUE))

notrus_to_chn <- artis %>%
  # Isolating Chinese imports that were NOT originally caught in Russia
  filter(source_country_iso3c != "RUS", importer_iso3c == "CHN") %>%
  group_by(year, sciname) %>%
  summarise(notrussia_live_t = sum(live_weight_t, na.rm = TRUE))

@@

@@

```{r}
rus_chn_usa <- artis %>%
  filter(source_country_iso3c == "RUS", exporter_iso3c == "CHN", importer_iso3c == "USA") %>%
  group_by(year, sciname) %>%
  summarise(live_weight_t = sum(live_weight_t, na.rm = TRUE)) %>%
  ungroup() %>%
  left_join(chn_to_usa %>%
            select(year, sciname, min_russia, max_russia)) %>%
  mutate(live_weight_t = live_weight_t / 1e3,
         min_russia = min_russia / 1e3,
         max_russia = max_russia / 1e3)

p1 <- rus_chn_usa %>% 
  filter(sciname == "gadus chalcogrammus",
         year > 1996) %>%
  ggplot(aes(x = year)) +
  geom_ribbon(aes(ymin = min_russia, ymax = max_russia), fill = "#86ADA7", alpha = 0.5) +
  geom_line(aes(y = live_weight_t)) +
  xlim(1997, 2020) +
  scale_y_continuous(position = "right") +
  labs(x = "", y = "tonnes, live weight") +#, title = "US imports of Russian Alaska pollock via China") +
  theme_bw() +
  theme(
    axis.title.y = element_blank(),
    axis.text.x = element_blank(),
    plot.margin = margin(l = 2, b = -2, unit = "mm")
  )

p2 <- rus_chn_usa %>%
  filter(year > 1996,
         sciname == "gadus morhua") %>%
  left_join(chn_to_usa %>%
              select(year, sciname, min_russia, max_russia)) %>% 
  ggplot(aes(x = year)) +
  geom_ribbon(aes(ymin = min_russia, ymax = max_russia), fill = "#86ADA7", alpha = 0.5) +
  geom_line(aes(y = live_weight_t)) +
  scale_y_continuous(position = "right") +
  xlim(1997, 2020) +
  labs(x = "", y = "tonnes, live weight") +#, title = "US imports of Russian Atlantic cod via China") +
  theme_bw() +
  theme(
    axis.title.y = element_blank(),
    axis.text.x = element_blank(),
    plot.margin = margin(r = 2, l = 2, b = -2, unit = "mm")
  )

p3 <- rus_chn_usa %>%
  filter(sciname == "oncorhynchus gorbuscha",
         year > 1996) %>%
  ggplot(aes(x = year)) +
  geom_ribbon(aes(ymin = min_russia, ymax = max_russia), fill = "#86ADA7", alpha = 0.5) +
  geom_line(aes(y = live_weight_t)) +
  scale_y_continuous(position = "right") +
  xlim(1997, 2020) +
  labs(x = "", y = "tonnes, live weight") +#, title = "US imports of Russian pink salmon via China") +
  theme_bw() +
  theme(
    axis.title.y = element_blank(),
    axis.text.x = element_blank(),
    plot.margin = margin(r = 2, l = 2, b = -2, unit = "mm")
  )

p4 <- rus_chn_usa %>%
  filter(sciname == "melanogrammus aeglefinus",
         year > 1996) %>%
  ggplot(aes(x = year)) +
  geom_ribbon(aes(ymin = min_russia, ymax = max_russia), fill = "#86ADA7", alpha = 0.5) +
  geom_line(aes(y = live_weight_t)) +
  scale_y_continuous(position = "right") +
  xlim(1997, 2020) +
  labs(x = "", y = "tonnes, live weight") +#, title = "US imports of Russian haddock via China") +
  theme_bw() +
  theme(
    axis.title.y = element_blank(),
    axis.text.x = element_blank(),
    plot.margin = margin(l = 2, b = -2, r = 1.5, unit = "mm")
  )

p5 <- rus_chn_usa %>%
  filter(sciname == "gadus macrocephalus",
         year > 1996) %>%
  ggplot(aes(x = year)) +
  geom_ribbon(aes(ymin = min_russia, ymax = max_russia), fill = "#86ADA7", alpha = 0.5) +
  geom_line(aes(y = live_weight_t)) +
  scale_y_continuous(position = "right") +
  xlim(1997, 2020) +
  labs(x = "", y = "tonnes, live weight") +#, title = "US imports of Russian Pacific cod via China") +
  theme_bw() +
  theme(
    axis.title.y = element_blank(),
    plot.margin = margin(t = -1, r = 2, l = 2, b = -2, unit = "mm")
  )

p_joined <- ggarrange(p1, p2, p3, p4, p5, ncol = 1)

# Top species US consumes sourced from Russia

species_rank_df <- consumption %>%
  filter(consumer_iso3c == "USA", source_country_iso3c == "RUS", year %in% 2015:2019) %>%
  mutate(path = case_when(
    exporter_iso3c == "RUS" ~ "Direct\nimport", 
    TRUE ~ "Import from\nintermediate partner"
  )) %>% 
  rename("importer_iso3c" = "consumer_iso3c",
         "live_weight_t" = "consumption_live_t") %>%
  mutate(common_name_hs_modified = case_when(
    common_name_hs_modified == "alaska pollock(=walleye poll.)" ~ "Alaska Pollock",
    common_name_hs_modified == "atlantic cod" ~ "Atlantic Cod",
    common_name_hs_modified == "pink(=humpback) salmon" ~ "Pink Salmon",
    common_name_hs_modified == "haddock" ~ "Haddock",
    common_name_hs_modified == "pacific cod" ~ "Pacific Cod",
    TRUE ~ common_name_hs_modified
  )) %>%
  mutate(common_name_hs_modified = gsub(" ", "\n", common_name_hs_modified)) %>%
  mutate(live_weight_t = live_weight_t / length(2015:2019)) %>%
  mutate(live_weight_t = live_weight_t / 1e3)

species_rank_1 <- species_rank_df %>%
  filter(common_name_hs_modified == "Alaska\nPollock") %>%
  mutate(dom_source == "") %>%
  plot_bar(bar_group = "common_name_hs_modified", fill_type = "path", top_n = 5) +
  xlim(0, 90) +
  theme(
    legend.position = "none",
    axis.text.x = element_blank(),
    axis.text.y = element_text(angle = 90, hjust = 0.5),
    plot.margin = margin(b = -2, unit = "mm")
  ) +
  labs(y = "", x = "", fill = "")

species_rank_2 <- species_rank_df %>%
  filter(common_name_hs_modified == "Atlantic\nCod") %>%
  plot_bar(bar_group = "common_name_hs_modified", fill_type = "path", top_n = 5) + 
  xlim(0, 90) +
  theme(
    legend.position = "none",
    axis.text.x = element_blank(),
    axis.text.y = element_text(angle = 90, hjust = 0.5),
    plot.margin = margin(b = -2, unit = "mm")
  ) +
  labs(y = "", x = "", fill = "")

species_rank_3 <- species_rank_df %>%
  filter(common_name_hs_modified == "Pink\nSalmon") %>%
  plot_bar(bar_group = "common_name_hs_modified", fill_type = "path", top_n = 5) + 
  xlim(0, 90) +
  theme(
    legend.position = "none",
    axis.text.x = element_blank(),
    axis.text.y = element_text(angle = 90, hjust = 0.5),
    plot.margin = margin(b = -2, unit = "mm")
  ) +
  labs(y = "", x = "", fill = "")

species_rank_4 <- species_rank_df %>%
  filter(common_name_hs_modified == "Haddock") %>%
  mutate(common_name_hs_modified = paste("\n", common_name_hs_modified, sep = "")) %>%
  plot_bar(bar_group = "common_name_hs_modified", fill_type = "path", top_n = 5) + 
  xlim(0, 90) +
  theme(
    legend.position = "none",
    axis.text.x = element_blank(),
    axis.text.y = element_text(angle = 90, hjust = 0.5),
    plot.margin = margin(b = -2, unit = "mm")
  ) +
  labs(y = "", x = "", fill = "")

species_rank_5 <- species_rank_df %>%
  filter(common_name_hs_modified == "Pacific\nCod") %>%
  plot_bar(bar_group = "common_name_hs_modified", fill_type = "path", top_n = 5) + 
  xlim(0, 90) +
  theme(
    legend.position = "bottom",
    axis.text.y = element_text(angle = 90, hjust = 0.5),
    axis.title.x = element_text(size = 7),
    legend.key.size = unit(1, units = "line"),
    plot.margin = margin(t = -2, b = -1, unit = "mm")
  ) +
  labs(y = "", x = "Avg. Consumption (1000 t) (2015-2019)", fill = "")

# Format Figure 2 together
fig2 <- ggarrange(
  species_rank_1, p1,
  species_rank_2, p2,
  species_rank_3, p3,
  species_rank_4, p4,
  species_rank_5, p5,
  ncol = 2, nrow = 5,
  widths = c(1, 2),
  heights = c(1, 1, 1, 1, 1),
  common.legend = TRUE,
  legend = "bottom"
  )

fig2

fig2 <- annotate_figure(
  fig2,
  right = text_grob("US Imports of Russian Species (1000 t, live weight)", rot = 270)
  )

fig2 <- ggarrange(
  rus_us_sankey,
  fig2,
  nrow = 2,
  heights = c(1, 2)
)

fig2

ggsave("fig2.png", device = "png", width = 6.5, height = 6)
```
